Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-09-05 review/response.Rmd

The tool is likely to be of interest to the R community.  Most of my comments are about the technical aspect of the content. The writing is overall good, but please see my comment under the "writing" regarding to the clarity of the text.

### Major comment

- "Sometimes, two optimisers can start with the same basis but finish with bases of opposite sign...However, this creates difficulties for comparing the optimisers since the end bases will be symmetric to the origin. A sign flipping step is conducted..." and the "Reconciling the orientation" section
  - For 1D projections, flipping the sign is sufficient. For p-D projections of $\mathbb{R}^n$​, one may need a little more. To my knowledge most index functions are invariant to any rotations that happens within the p-subspace. This makes me wonder that in general, one may want to align two bases so that their difference does not contain any "within-subspace" components. In other words, one may want to compare representations in the Grassmannian manifold  (space of k-subspaces) instead of in the Stiefel manifold (space of orthonormal k-frames).

\textcolor{red}{With p-D bases, the correction of orientation is a bit more complicated. Take 2D as an example, two bases can be aligned in the first axis but not in the second. This would means there are $2^p$ possibility to check.}

@@

### Minor comment

- The software seems to be specific to projection pursuit. I wish the authors could comment more on its potential generality to other optimizations. For example, can one generalizes the tour method to visualize any parameter trace of an optimizer?

\textcolor{red}{It is feasible to generalise the tour method for diagnosing other optimisers, providing the parameter space can be simulated. In our examples, the parameter to trace (projection base ($p \times d$) ) lives in an p-sphere, which can be simulated by the `geozoo` package. For other optimisers, reserachers need first to create a data collection object in a tibble that track the parameter during the optimisation, and then to use ferrn to produce the diagnostic plots as shown in the paper.}

@@

- Figure 4 "...All the bases in PD have been flipped for easier comparison of the final bases..."
  - This is related to the major comment. In the figure, PD flipped in sign but stopped at a basis representation similar to the destination of the CRS. Flipping the sign back, does it mean that PD and CRS diverged but stopped at the similar subspace with opposite basis representations? Also, given that PD and CRS have the same starting bases and one is flipped, why wouldn't the dashed line pass the origin (gray dot) in the figure?

\textcolor{red}{Yes the reviewer is giving a decent explanation in describing the effect of flipping. The gray dot should land on the dashed line and this is a mistake due to the data not being updated after flipping in the code. This has now been corrected.}

- "Recall that the columns in a 2D basis are orthogonal to each other, so the space of *p* × 2 bases is a *p*-D torus".

  - It is not clear to me why "so". For p=2, the space of 2x2 bases is a pair of 1-D tori instead of just one (because you have two orientations for a pair of orthogonal vectors), right? For p=3, the space of 3x2 bases is SO(3), which is not a 3-D torus? Ref: https://en.wikipedia.org/wiki/Stiefel_manifold

\textcolor{red}{We change the wording of the sentence to "**a torus in the $p$-D space**"}

@@

### Writing

- "Along with the bases recorded during the optimisation and a zero basis, the parameters (centre and radius) of the 2D space can be estimated by PCA. The centre of the circle is the first two PC coordinates of the zero matrix, and the radius is estimated as the largest distance from the centre to the basis."
  - It took me multiple passes to get what this means. Perhaps instead starting with something like: "We use PCA to project and visualize the parameters/bases in 2D. The centre of the 2D view is..."?

\textcolor{red}{Changed to "We use PCA to estimate the 2D space that contains all the bases recorded and the zero basis. The centre of the 2D view is the first two PC coordinates of the zero matrix, and the radius is estimated as the largest distance from the centre to the basis."}

@@

- "Figure 6 shows some frames from the tour plot of the same two optimisations in its original 5D space."
  - I think this is the first mention of "5D space"/5D data in the main text (apart from the caption in Figure 4), so it may be worth clarifying what the original 5D space is.

\textcolor{red}{The explanation of data set is introduced in the subsection *Simulation setup* under *Diagnosing an optimiser*. To avoid ambiguity, we change the "original 5D space" to "original space" and give more details about the original space in the figure caption: "The basis space in this example is a 5D unit sphere ...".}

@@

- "While the previous few examples have looked at the space of 1D bases ...  2D bases"
  - I don't think the terms "1D bases" and "2D bases" are standard. Perhaps (orthonormal) "1-frames" and "2-frames"?

\textcolor{red}{Changed to "While the previous few examples have looked at the space of 1-frames in a unit sphere, this section visualises the space of 2-frames."}

@@

# Reviewer 2

These experiments are interesting and so is the methodology.
The conclusions could do with beefing up
What can we learn about how to optimise the holes index for 1 and 2d?
Does this apply to other smooth indices? What about non-smooth indices?
What about indices in other dimensions?

\textcolor{red}{A paragraph summarising the finding is added as the second paragram in the conclusion}

@@

1. Should refer to earlier work on scagnostic indices, page 3

\textcolor{red}{Added reference of (Wilkinson et al., 2005) and  (Wilkinson and Wills, 2008):}

\textcolor{red}{L. Wilkinson and G. Wills. Scagnostics distributions. Journal of Computational and Graphical Statistics, 17 (2):473–491, 2008}

\textcolor{red}{L. Wilkinson, A. Anand, and R. Grossman. Graph-theoretic scagnostics. In IEEE Symposium on Information Visualization, 2005. INFOVIS 2005., pages 157–164, Oct 2005.}

@@

2. figure 2 caption "using the holes index"  "and a boxplot". What is the colour scale for the points? The text related to figure 2 in the bottom of page 5 should mention the dataset and the index, giving references if needed.

\textcolor{red}{Fixed language. Added mention the color scale in the figure 2 caption:  "The color scale is from the customised botanical palette in the ferrn package."}

@@

4. In Figure 3 would be better if the y-axes scales were the same for the two graphs.

\textcolor{red}{fixed}

5. What is the star in figures 4 and 5? This is not mentioned in the text or caption

\textcolor{red}{Added "The black star represents the theoretical best basis the optimisers aiming to find." in the caption of figure 4.}

@@

6. In the text you say things like "details=TRUE" and "animate=TRUE" but what functions are you referring to?

\textcolor{red}{Mention of "details=TRUE" and "animate=TRUE" is removed from subsection diagnostic 3a and 3b to the implementation section: `explore\_space\_pca()` produces the PCA plot of projection bases on the reduced space. Figure 4 includes the additional details of anchor and search bases, which can be turned on by the argument `details = TRUE`. The animated version in Figure 5 is produced with argument `animate = TRUE`.}

@@

7. In Figure 9, it seems CRS is doing better here than in Figure 8-- maybe this could be mentioned.

\textcolor{red}{Figure 8 and 9 focuses on different aspects: Figure 8 compares the effect of implementing an interruption while Figure 9 compares the effect of polishing. Cross comparing the two experiments is less meaningful.}

@@

8. "not the case for all the indexes" missing a "." page 11

\textcolor{red}{added}

9. For the Kolmogorov index, why are you using randomly generated data instead of normal quantiles?

\textcolor{red}{The Kolmogorov Smirnoff index here looks at the difference between a theoretical pdf and an empirical one based on data. I am not sure what would be the reasoning for using normal quantiles in this index. That would imply you are assuming normality on the theoretial pdf.}

### 2021-09-05 paper/zhang-cook-laa-langrene-menendez.Rmd
tweak gif for html rendering

---
title: "Visual Diagnostics for Constrained Optimisation with Application to Guided Tours"
author:
  - name: H.Sherry Zhang
    affiliation: Monash University 
    address: Department of Econometrics and Business Statistics 
    url: Melbourne, Australia
    email:  huize.zhang@monash.edu
  - name: Dianne Cook
    affiliation: Monash University 
    address: Department of Econometrics and Business Statistics
    url: Melbourne, Australia
    email:  dicook@monash.edu
  - name: Ursula Laa
    affiliation: University of Natural Resources and Life Sciences
    address: Institute of Statistics
    url: Vienna, Austria
    email:  ursula.laa@boku.ac.at  
  - name: Nicolas Langrené
    affiliation: CSIRO Data61 
    address: 34 Village Street, Docklands VIC 3008 Australia
    url: Melbourne, Australia
    email: nicolas.langrene@csiro.au
  - name: Patricia Menéndez
    affiliation: Monash University 
    address: Department of Econometrics and Business Statistics
    url: Melbourne, Australia
    email:  patricia.menendez@monash.edu 
abstract: >
  A guided tour helps to visualise high-dimensional data by showing low-dimensional projections along a projection pursuit optimisation path. Projection pursuit is a generalisation of principal component analysis, in the sense that different indexes are used to define the interestingness of the projected data. While much work has been done in developing new indexes in the literature, less has been done on understanding the optimisation. Index functions can be noisy, might have multiple local maxima as well as an optimal maximum, and are constrained to generate orthonormal projection frames, which complicates the optimization. In addition, projection pursuit is primarily used for exploratory data analysis, and finding the local maxima is also useful. The guided tour is especially useful for exploration, because it conducts geodesic interpolation connecting steps in the optimisation and shows how the projected data changes as a maxima is approached. This work provides new visual diagnostics for examining a choice of optimisation procedure, based on the provision of a new data object which collects information throughout the optimisation. It has helped to diagnose and fix several problems with projection pursuit guided tour. This work might be useful more broadly for diagnosing optimisers, and comparing their performance. The diagnostics are implemented in the R package \pkg{ferrn}.
keywords: graphics, multivariate, optimization
preamble: >
  \usepackage{mathtools}
  \usepackage[ruled, linesnumbered]{algorithm2e}
output: 
  rjtools::rjournal_web_article
bibliography: zhang-cook-laa-langrene-menendez.bib
---

@@

Let $\mathbf{X}_{n \times p}$ be the data matrix with $n$ observations in $p$ dimensions. A $d$-dimensional projection is a linear transformation from $\mathbb{R}^p$ into $\mathbb{R}^d$ defined as $\mathbf{Y} = \mathbf{X} \cdot \mathbf{A}$, where $\mathbf{Y}_{n \times d}$ is the projected data and $\mathbf{A}_{p\times d}$ is the projection matrix. We define $f: \mathbb{R}^{n \times d} \mapsto \mathbb{R}$ to be an index function that maps the projected data $\mathbf{Y}$ onto a scalar value. This is commonly known as the projection pursuit index function, or just index function, and is used to measure the "interestingness" of a given projection. An interesting projection shows structures that are non-normal since theoretical proofs from @diaconis1984asymptotics have shown that projections tend to be normal, as $n$ and $p$ approach infinity under certain conditions. There have been many index functions proposed in the literature, here are a few examples: early indexes that can be categorised as measuring the $L^2$ distance between the projection and a normal distribution: Legendre index [@friedman1974projection], Hermite index [@hall1989polynomial], and natural Hermite index [@cook1993projection]; chi-square index [@posse1995projection] for detecting spiral structure; LDA index [@lee2005projection] and PDA [@lee2010projection] index for supervised classification; kurtosis index [@Loperfido2020] and skewness index [@Loperfido2018] for detecting outliers in financial time series; and most recently, scagnostic indexes [@laa2020using] for summarising structures in scatterplot matrices based on eight scagnostic measures [@scag,@WW08].

@@

```{r toy-pca, fig.height = 4, fig.asp = 1, fig.cap = "Search paths of CRS (green) and PD (brown) in the PCA-reduced basis space for 1D projection problem on the five-variable dataset, \\code{boa5} using holes index. The basis space, a 5D unit sphere, is projected onto a 2D circle by PCA. The black star is the theoretical best basis the optimisers aiming to find. All the bases in PD have been flipped for easier comparison of the final bases and a grey dashed line has been annotated to indicate the symmetry of the two start bases."}
```

@@

```{r toy-pca-animated, fig.cap = "Six frames selected from the animated version of the previous plot. With animation, the progression of the search paths from start to finish is better identified. CRS (green) finishes the optimisation quicker than PD (brown) since there is no further movement for CRS in the sixth frame. The full video of the animation can be found at \\url{https://vimeo.com/504242845}.", eval=knitr::is_latex_output()}
```

```{r toy-pca-animated-interactive, fig.height = 7, fig.width = 7, fig.cap = "this is the interactive version", eval=knitr::is_html_output()}
```

@@

```{r toy-tour, fig.cap="Six frames selected from rotating the high-dimensional basis space, along with the same two search paths from Figure \\ref{fig:toy-pca} and \\ref{fig:toy-pca-animated}. The basis space in this example is a 5D unit sphere, on which points (grey) are randomly generated via the CRAN package geozoo. The full video of the animation can be found at \\url{https://vimeo.com/512885379}."}
```

@@

```{r toy-torus, fig.cap="Six frames selected from rotating the 2D basis space along with two search paths optimised by PD (brown) and CRS (green). The projection problem is a 2D projection with three variables using the holes index. The grey points are randomly generated 2D projection bases in the space and it can be observed that these points form a torus. The full video of the animation can be found at \\url{https://vimeo.com/512882784}.", eval = knitr::is_latex_output()}
```

```{r toy-torus-interactive, out.height = "10%", out.width = "10%", fig.cap="Six frames selected from rotating the 2D basis space along with two search paths optimised by PD (brown) and CRS (green). The projection problem is a 2D projection with three variables using the holes index. The grey points are randomly generated 2D projection bases in the space and it can be observed that these points form a torus. The full video of the animation can be found at \\url{https://vimeo.com/512882784}.", eval = knitr::is_html_output()}
```

@@

  - \code{explore\_trace\_search()} produces summary plots in Figure \ref{fig:toy-search}.
  - \code{explore\_trace\_interp()} produces trace plots for the interpolation points in Figure \ref{fig:toy-interp}.
  - \code{explore\_space\_pca()} produces the PCA plot of projection bases on the reduced space in Figure \ref{fig:toy-pca}. The animated version in Figure \ref{fig:toy-pca-animated} can be turned on via the argument `animate = TRUE`.
   - \code{explore\_space\_pca()} produces the PCA plot of projection bases on the reduced space. Figure \ref{fig:toy-pca} includes the additional details of anchor and search bases, which can be turned on by the argument `details = TRUE`. The animated version in Figure \ref{fig:toy-pca-animated} is produced with argument `animate = TRUE`.
  - \code{explore\_space\_tour()} produces animated tour view on the full space of the projection bases in Figure \ref{fig:toy-tour}.

- \code{get\_*()} extracts and manipulates certain components from the existing data object.
  - \code{get\_anchor()} extracts target observations 
  - \code{get\_basis\_matrix()} flattens all the bases into a matrix
  - \code{get\_best()} extracts the observation with the highest index value in the data object
  - \code{get\_dir\_search()} extracts directional search observations for PD search
  - \code{get\_interp()} extracts interpolated observations
  - \code{get\_interp\_last()} extracts the ending interpolated observations in each iteration
  - \code{get\_interrupt()} extracts the ending interpolated observations and the target observations if  the interpolation is interrupted
  - \code{get\_search()} extracts search observations 
  - \code{get\_search\_count()} extracts the count of search observations 
  - \code{get\_space\_param()} produces the coordinates of the centre and radius of the basis space
  - \code{get\_start()} extracts the starting observation
  - \code{get\_theo()} extracts the theoretical best observations, if given

- \code{bind\_*()} incorporates additional information outside the tour optimisation into the data object.
  - \code{bind\_theoretical()} binds the theoretical best observation in simulated experiment
  - \code{bind\_random()} binds randomly generated bases in the projection bases space to the data object
  - \code{bind\_random\_matrix()} binds randomly generated bases and outputs in a matrix format

- \code{add\_*()} provides wrapper functions to create ggprotos for different components for the PCA plot
  - \code{add\_anchor()} for plotting anchor bases
  - \code{add\_anno()} for annotating the symmetry of start bases
  - \code{add\_dir\_search()} for plotting the directional search bases with magnified distance
  - \code{add\_end()} for plotting end bases
  - \code{add\_interp()} for plotting the interpolation path
  - \code{add\_interp\_last()} for plotting the last interpolation bases for comparing with target bases when interruption is used
  - \code{add\_interrupt()} for linking the last interpolation bases with target ones when interruption is used
  - \code{add\_search()} for plotting search bases
  - \code{add\_space()} for plotting the circular space 
  - \code{add\_start()} for plotting start bases
  - \code{add\_theo()} for plotting theoretical best bases, if applicable

- Utilities
  - \code{theme\_fern()} and \code{format\_label()} for better display of the grid lines and axis formatting
  - \code{clean\_method()} to clean up the name of the optimisers
  - \code{botanical\_palettes} is a collection of colour palettes from Australian native plants. Quantitative palettes include daisy, banksia, and cherry and sequential palettes contain fern and acacia
  - \code{botanical\_pal()} as the colour interpolator 
  - \code{scale\_color\_*()} and \code{scale\_fill\_*()} for scaling the colour and fill of the plot

@@

>>>>

---
title: "Visual Diagnostics for Constrained Optimisation with Application to Guided Tours"
author:
  - name: H.Sherry Zhang
    affiliation: Monash University 
    address: Department of Econometrics and Business Statistics 
    url: Melbourne, Australia
    email:  huize.zhang@monash.edu
  - name: Dianne Cook
    affiliation: Monash University 
    address: Department of Econometrics and Business Statistics
    url: Melbourne, Australia
    email:  dicook@monash.edu
  - name: Ursula Laa
    affiliation: University of Natural Resources and Life Sciences
    address: Institute of Statistics
    url: Vienna, Austria
    email:  ursula.laa@boku.ac.at  
  - name: Nicolas Langrené
    affiliation: CSIRO Data61 
    address: 34 Village Street, Docklands VIC 3008 Australia
    url: Melbourne, Australia
    email: nicolas.langrene@csiro.au
  - name: Patricia Menéndez
    affiliation: Monash University 
    address: Department of Econometrics and Business Statistics
    url: Melbourne, Australia
    email:  patricia.menendez@monash.edu 
abstract: >
  A guided tour helps to visualise high-dimensional data by showing low-dimensional projections along a projection pursuit optimisation path. Projection pursuit is a generalisation of principal component analysis, in the sense that different indexes are used to define the interestingness of the projected data. While much work has been done in developing new indexes in the literature, less has been done on understanding the optimisation. Index functions can be noisy, might have multiple local maxima as well as an optimal maximum, and are constrained to generate orthonormal projection frames, which complicates the optimization. In addition, projection pursuit is primarily used for exploratory data analysis, and finding the local maxima is also useful. The guided tour is especially useful for exploration, because it conducts geodesic interpolation connecting steps in the optimisation and shows how the projected data changes as a maxima is approached. This work provides new visual diagnostics for examining a choice of optimisation procedure, based on the provision of a new data object which collects information throughout the optimisation. It has helped to diagnose and fix several problems with projection pursuit guided tour. This work might be useful more broadly for diagnosing optimisers, and comparing their performance. The diagnostics are implemented in the R package [ferrn](https://github.com/huizezhang-sherry/ferrn).
keywords: graphics, multivariate, optimization
preamble: >
  \usepackage{mathtools}
  \usepackage[ruled, linesnumbered]{algorithm2e}
output: 
  rjtools::rjournal_web_article
bibliography: zhang-cook-laa-langrene-menendez.bib
---

@@

Let $\mathbf{X}_{n \times p}$ be the data matrix with $n$ observations in $p$ dimensions. A $d$-dimensional projection is a linear transformation from $\mathbb{R}^p$ into $\mathbb{R}^d$ defined as $\mathbf{Y} = \mathbf{X} \cdot \mathbf{A}$, where $\mathbf{Y}_{n \times d}$ is the projected data and $\mathbf{A}_{p\times d}$ is the projection matrix. We define $f: \mathbb{R}^{n \times d} \mapsto \mathbb{R}$ to be an index function that maps the projected data $\mathbf{Y}$ onto a scalar value. This is commonly known as the projection pursuit index function, or just index function, and is used to measure the "interestingness" of a given projection. An interesting projection shows structures that are non-normal since theoretical proofs from @diaconis1984asymptotics have shown that projections tend to be normal, as $n$ and $p$ approach infinity under certain conditions. There have been many index functions proposed in the literature, here are a few examples: early indexes that can be categorised as measuring the $L^2$ distance between the projection and a normal distribution: Legendre index [@friedman1974projection], Hermite index [@hall1989polynomial], and natural Hermite index [@cook1993projection]; chi-square index [@posse1995projection] for detecting spiral structure; LDA index [@lee2005projection] and PDA [@lee2010projection] index for supervised classification; kurtosis index [@Loperfido2020] and skewness index [@Loperfido2018] for detecting outliers in financial time series; and most recently, scagnostic indexes [@laa2020using] for summarising structures in scatterplot matrices based on eight scagnostic measures [@scag; @WW08].

@@

```{r toy-pca, fig.height = 4, fig.asp = 1, fig.cap = "Search paths of CRS (green) and PD (brown) in the PCA-reduced basis space for 1D projection problem on the five-variable dataset, \\code{boa5} using holes index. The basis space, a 5D unit sphere, is projected onto a 2D circle by PCA. The black star represents the theoretical best basis the optimisers aiming to find. All the bases in PD have been flipped for easier comparison of the final bases and a grey dashed line has been annotated to indicate the symmetry of the two start bases."}
```

@@

```{r toy-pca-animated, fig.cap = "Six frames selected from the animated version of the previous plot. With animation, the progression of the search paths from start to finish is better identified. CRS (green) finishes the optimisation quicker than PD (brown) since there is no further movement for CRS in the sixth frame. The full video of the animation can be found in the html version of the paper.", eval=knitr::is_latex_output()}
```

```{r toy-pca-animated-interactive,  out.wdith= "100px", fig.cap = "Animated version of Figure \\ref{fig:toy-pca}. With animation, the progression of the search paths from start to finish can better identified and CRS (green) finishes the optimisation quicker than PD (brown).", eval=knitr::is_html_output()}
```

@@

```{r toy-tour, fig.cap="Six frames selected from rotating the high-dimensional basis space, along with the same two search paths from Figure \\ref{fig:toy-pca} and \\ref{fig:toy-pca-animated}. The basis space in this example is a 5D unit sphere, on which points (grey) are randomly generated via the CRAN package geozoo. The full animation can be seen in the html version of the paper."}
```

```{r toy-tour-interactive, fig.cap="Animating the two paths from Figure \\ref{fig:toy-pca} and \\ref{fig:toy-pca-animated} in the full basis space. The full basis space in this example is a 5D unit sphere, on which points (grey) are randomly generated via the CRAN package geozoo."}
```

@@

```{r toy-torus, fig.cap="Six frames selected from rotating the 2D basis space along with two search paths optimised by PD (brown) and CRS (green). The projection problem is a 2D projection with three variables using the holes index. The grey points are randomly generated 2D projection bases in the space and it can be observed that these points form a torus. The full video of the animation can be found in the html version of the paper.", eval = knitr::is_latex_output()}
```

```{r toy-torus-interactive, fig.cap="Animation of rotating the 2D basis space along with two search paths optimised by PD (brown) and CRS (green). The projection problem is a 2D projection with three variables using the holes index. The grey points are randomly generated 2D projection bases in the space and it can be observed that these points form a torus.", eval = knitr::is_html_output()}
```

@@

  - `explore_trace_search()` produces summary plots in Figure \ref{fig:toy-search}.
  - `explore_trace_interp()` produces trace plots for the interpolation points in Figure \ref{fig:toy-interp}.
  - `explore_space_pca()` produces the PCA plot of projection bases on the reduced space in Figure \ref{fig:toy-pca}. The animated version in Figure \ref{fig:toy-pca-animated} can be turned on via the argument `animate = TRUE`.
   - `explore_space_pca()` produces the PCA plot of projection bases on the reduced space. Figure \ref{fig:toy-pca} includes the additional details of anchor and search bases, which can be turned on by the argument `details = TRUE`. The animated version in Figure \ref{fig:toy-pca-animated} is produced with argument `animate = TRUE`.
  - `explore_space_tour()` produces animated tour view on the full space of the projection bases in Figure \ref{fig:toy-tour}.

- `get_*()` extracts and manipulates certain components from the existing data object.
  - `get_anchor()` extracts target observations 
  - `get_basis_matrix()` flattens all the bases into a matrix
  - `get_best()` extracts the observation with the highest index value in the data object
  - `get_dir_search()` extracts directional search observations for PD search
  - `get_interp()` extracts interpolated observations
  - `get_interp_last()` extracts the ending interpolated observations in each iteration
  - `get_interrupt()` extracts the ending interpolated observations and the target observations if  the interpolation is interrupted
  - `get_search()` extracts search observations 
  - `get_search_count()` extracts the count of search observations 
  - `get_space_param()` produces the coordinates of the centre and radius of the basis space
  - `get_start()` extracts the starting observation
  - `get_theo()` extracts the theoretical best observations, if given

- `bind_*()` incorporates additional information outside the tour optimisation into the data object.
  - `bind_theoretical()` binds the theoretical best observation in simulated experiment
  - `bind_random()` binds randomly generated bases in the projection bases space to the data object
  - `bind_random_matrix()` binds randomly generated bases and outputs in a matrix format

- `add_*()` provides wrapper functions to create ggprotos for different components for the PCA plot
  - `add_anchor()` for plotting anchor bases
  - `add_anno()` for annotating the symmetry of start bases
  - `add_dir_search()` for plotting the directional search bases with magnified distance
  - `add_end()` for plotting end bases
  - `add_interp()` for plotting the interpolation path
  - `add_interp_last()` for plotting the last interpolation bases for comparing with target bases when interruption is used
  - `add_interrupt()` for linking the last interpolation bases with target ones when interruption is used
  - `add_search()` for plotting search bases
  - `add_space()` for plotting the circular space 
  - `add_start()` for plotting start bases
  - `add_theo()` for plotting theoretical best bases, if applicable

- Utilities
  - `theme_fern()` and `format_label()` for better display of the grid lines and axis formatting
  - `clean_method()` to clean up the name of the optimisers
  - `botanical_palettes()` is a collection of colour palettes from Australian native plants. Quantitative palettes include daisy, banksia, and cherry and sequential palettes contain fern and acacia
  - `botanical_pal()` as the colour interpolator 
  - `scale_color_*()` and `scale_fill_*()` for scaling the colour and fill of the plot

@@

Experiments in this paper have shown that random search algorithms tend to require larger search size for 2D indexes as compared to 1D indexes. All the three optimisers tend to work well for smooth indexes while PD fails generally fails for non-smooth indexes. This is due to the fact that derivative based methods are in general not suitable for optimising non-smooth functions.
